Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and its audio-description

### 2020-10-13 paper/main.tex
discussion: stability of contrast madness

@@

\subsubsection{PPA}
% PPA AO
Regarding contrasts of the AO stimulus, six of eight contrasts show
significant bilateral clusters in the anterior part of the group PPA.
% PPA AV
Regarding contrasts of the AV stimulus, x of y contrasts show significant
bilateral clusters in the PPA but extending into posterior regions
% no incidental findings
Results of the additional contrasts suggest that bilaterally increased
activation in the PPA does not depend on accidental findings but is are stable
across contrasts of the movie and the audio-description.
% anterior vs. posterior?

\subsubsection{localization performance and noise}
% overall good isolation;  whole brain analysis and not many random clusters
Despite performing a whole brain analysis on naturalistic stimuli with many
uncontrolled stimuli we do not find many random clusters in single contrasts or
even systematically across contrasts\todo{good god but that's essentially it}.
% shit was averaged out we did not even know of
Further, unknown stimulus features we did not even annotate did not lead to a
variety of significant cluster across the brain that hamper interpretation of
results.
% movie: attention, and shit
\todo[inline]{where are no clusters? e.g. top-down / bottom-up
attention, eye movements (FEF) (cf. corbetta2002control) or memory (which
memory)?}

% BUT: amount of data
Nevertheless, localization performance depends on the amount of available
data\todo{give examples of contrast using less events in AV and AO}.
% BUT: match of the stimulus type/averaged events
Further, localization performance is also influenced by how well events
within categories matched on average the preferred stimulus type.
% AV: frame content
In the AV stimulus, we averaged different kind of movie cuts regardless to the
movie frames content.
\todo[inline]{how well spatially constrained are the clusters?}
% AO: stimulus categories
Moreover, nouns of the narrator cueing a switch to another setting are often
forestalled by changes of the soundscape.\todo{cross-modal control contrasts;
all negative results at moment of cuts but vse\_new > pe\_old): right RSC.}
% arnott
\todo[inline]{e.g. arnott2008crinkling find increased activations of PPA to
sound made by objects}
% hypothesis
We hypothesize that not just semantic information but also the mere changes of a
soundscape that cues a listener about a setting's spatial layout of could
correlate with increased activity in the PPA.
% AO: superior temporal cortex
Nevertheless in four of nine contrasts of the AO stimulus, we find significant
clusters in superior auditory cortices (including early auditory
cortices?)\todo{which exactly}
% conclusion
This suggests that variance correlating with lower level auditory processes was
(not) averaged (out) across trials\todo{which contrasts; A1 \& low-level
nuisance regressors?}

% conclusion: AO and AV stability
In summary, our results across add further evidence that model-driven analyses
can be run on data from naturalistic stimuli to isolate brain activity
correlating with specific perceptual processes.
% but
Nevertheless isolation performance relies on how well the model captures
different aspects of the stimuli's feature space.

>>>>

\todo[inline]{the pain starts exactly here}

@@

\subsubsection{PPA}
% PPA AO
Regarding contrasts of the AO stimulus, six of eight contrasts show
significant bilateral clusters in the anterior part of the group PPA.
% PPA AV
Regarding contrasts of the AV stimulus, all five contrasts show significant
bilateral clusters in the PPA but extending into posterior regions
% no incidental findings
Results of the additional contrasts suggest that bilaterally increased
activation in the PPA does not depend on accidental findings but is are stable
across contrasts of the movie and the audio-description.

% but
Nevertheless, results suggest that localization performance depends on the
amount of available data and how well the feature space is modeled.
% what's going on
Despite performing a whole brain analysis, we do not find many (random) clusters
in single contrasts or even systematically across contrasts that hamper the
interpretation of results.\todo[inline]{god forgive me for this paragraph}.

% other clusters
\todo[inline]{where are no clusters? e.g. top-down / bottom-up
attention, eye movements (FEF) (cf. corbetta2002control) or memory (which
memory)?}

% BUT: amount of data
Nevertheless, localization performance is influenced on the amount of available
data\todo{give examples of contrast using less events in AV and AO} and well
events within categories matched on average the preferred stimulus type.
% example AV: data amount and category homogeneity
For example in the AV stimulus, we averaged different kind of movie cuts
regardless to the movie frames content.\todo[inline]{how well spatially
constrained are the clusters?}
% AO: stimulus categories
For example in the AO stimulus, nouns of the narrator that cue a switch to
another setting belong to different categories (s. above).
% AO: number of events
\todo[inline]{Number of events in which contrasts?}
% example for data amount AO: superior temporal cortex
In four of nine contrasts of the AO stimulus, we find significant
clusters in superior auditory cortices (including early auditory
cortices?)\todo{which exactly}
% conclusion
This suggests that variance correlating with lower level auditory processes was
(not) averaged (out) across trials\todo{which contrasts; A1 \& low-level
nuisance regressors?}
% foreshadowing of narrator by soundscape
Further, verbal cues are regularly forestalled by changes of the
soundscape.\todo{cross-modal control contrasts; all negative results at moment
of cuts but vse\_new > pe\_old): right RSC.}
% arnott
\todo[inline]{e.g. arnott2008crinkling find increased activations of PPA to
sound made by objects}
% hypothesis
We hypothesize that not just semantic information but also the mere changes of a
soundscape that cues a listener about a setting's spatial layout of could
correlate with increased activity in the PPA.
% conclusion: AO and AV stability
In summary, our results across add further evidence that model-driven analyses
can be run on data from naturalistic stimuli to isolate brain activity
correlating with specific perceptual processes.
% but
Nevertheless isolation performance relies on how well the model captures
different aspects of the stimuli's feature space.
